\subsection{Subtasks}
    \begin{itemize}
        \item Create a Monitor package including classes used by the image analysis and the hardware systems. Implement Observer-Observable and real time behaviour. \textbf{Estimated deadline}: 8/11
        \item Assemble the robot arm. \textbf{Estimated deadline}: 12/11
        \item Set up a display in such a way that the cameras and the robot arm have stationary positions. \textbf{Estimated deadline}: 12/11
        \item Implement communication between arduino and PC. \textbf{Estimated deadline}: 12/11
        \item Find mathematical model for how the ball trajectory should be estimated. Implement this into the ballTrajectory package. \textbf{Estimated deadline}: 15/11
        \item Find a model for the arm trajectory. \textbf{Estimated deadline}: 19/11 
        
        \item Create a package for how the servos should respond to the given arm trajectory. \textbf{Estimated deadline}: 19/11
        \item Perform image segmentation to find the ball in the two cameras. \textbf{Estimated deadline}: 3/12
        \item Make a computer vision system to map the ball segments in the images to a 3D-coordinate. Including calibration and on-line calculations. \textbf{Estimated deadline}: 3/12
        \item (Optional); Implement feedback control of robot arm position \textbf{Estimated deadline}: N/A
    \end{itemize}
    
\subsection{Important dates}
    \begin{itemize}
        \item 10/11 -  Hand in project plan.
        \item 19/11 - Feedback seminar 1 on the modeling and design.
        \item x/11 - Report should be pushed to git to allow peer review by other groups.
        \item 10/12 - Feedback seminar 2 on the design and implementation.
        \item 17/12 - The whole process should be finished and ready for demonstration.
        \item 20/12 - A complete project report should be pushed to git and the supervisor notified.
        \item /1 - A final revised report should be pushed to git and the supervisor notified.
        \item x/1 - Project presentation and demonstration.
    \end{itemize}
